\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-18 paper/paper.tex
final? :)

\ednote{DENIS DOES THIS.}

@@

\subsection{ROS \& Octomap}
For this research project we will make use of the Robot Operating System (ROS). ROS is a framework for creating robot software.  Within ROS, this project will use the octomap\_server \cite{hornung13auro}.\\

@@

>>>>

The mapping of underwater structures is a common task in underwater robotics. Yet, only a few papers deal with the actual algorithm of mapping structures which is used to guide robots during their exploration. Therefore we could not find much previous work, especially none which deals with guidance algorithms for the mapping of a horizontal structure via an autonomous underwater robot.\\

One paper that deals with an actual guiding algorithm is \textit{A behavior-based architecture for autonomous underwater exploration} \cite{rosenblatt2002behavior}. There the authors use a behavior-based control architecture to safely guide a robot through a reef. Their robot follows a rope on the sea floor by utilizing a camera to get optical input. The rope acts as a tool for collision avoidance and path planning as it can be safely laid out by humans beforehand.\\

In another work, \textit{3-D terrain covering and map building algorithm for an AUV} \cite{lee20093}, the authors deal with the guidance and the mapping of an ocean floor with multiple islands or underwater mountains around. The approach they use is to explore the whole space by iteratively exploring a plane for each depth level. The situation and the approach used are drastically different from what we try to do as we try to scan horizontal structures and we do this using an improved interative approach.\\

There are many other papers that deal with cooperative exploration of multiple robots and the path planning for those robots. This does not apply well to our problem though, as we are only dealing with one robot and do not have to account for problems and challenges like the optimal division of work \cite{wu2012robust}. Most other papers which deal with actual guidance algorithms do so in combination with related mapping techniques like SLAM (e.g. \cite{makarenko2002experiment}).\\

@@

\subsection{ROS \& Octomap}
For this research project we will make use of the Robot Operating System (ROS). ROS is a collection of frameworks for the development of robot control software. It provides us with many packages that implement functionalities like point cloud publishing and the simulation of different sensors. Within ROS, this project will use the octomap\_server \cite{hornung13auro}.\\

@@

\begin{wrapfigure}{c}{\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.70\textwidth]{assets/robot.png}
    }
  \end{center}
\vspace{-20pt}
  \caption{Basic Algorithm}
  \label{fig:basicAlgorithm}
\end{wrapfigure}
